\documentclass[12pt, letterpaper, preprint]{aastex62}
\input{vc}
%\usepackage[breaklinks,colorlinks, urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{color}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{ctable}
\usepackage{bm}
\usepackage[normalem]{ulem} % Added by MS for \sout -> not required for final version
\usepackage{xspace}
\usepackage{csvsimple} 

% typesetting shih
\linespread{1.08} % close to 10/13 spacing
\setlength{\parindent}{1.08\baselineskip} % Bringhurst
\setlength{\parskip}{0ex}
\let\oldbibliography\thebibliography % killin' me.
\renewcommand{\thebibliography}[1]{%
  \oldbibliography{#1}%
  \setlength{\itemsep}{0pt}%
  \setlength{\parsep}{0pt}%
  \setlength{\parskip}{0pt}%
  \setlength{\bibsep}{0ex}
  \raggedright
}
\setlength{\footnotesep}{0ex} % seriously?

% citation alias

% math shih
\newcommand{\setof}[1]{\left\{{#1}\right\}}
\newcommand{\given}{\,|\,}
\newcommand{\lss}{{\small{LSS}}\xspace}

\newcommand{\Om}{\Omega_{\rm m}} 
\newcommand{\Ob}{\Omega_{\rm b}} 
\newcommand{\OL}{\Omega_\Lambda}
\newcommand{\smnu}{M_\nu}
\newcommand{\sig}{\sigma_8} 
\newcommand{\mmin}{M_{\rm min}}
\newcommand{\BOk}{\widehat{B}_0} 
\newcommand{\hmpc}{\,h/\mathrm{Mpc}}
\newcommand{\bfi}[1]{\textbf{\textit{#1}}}
\newcommand{\parti}[1]{\frac{\partial #1}{\partial \theta_i}}
\newcommand{\partj}[1]{\frac{\partial #1}{\partial \theta_j}}
\newcommand{\mpc}{h/{\rm Mpc}}

\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
% text shih
\newcommand{\foreign}[1]{\textsl{#1}}
\newcommand{\etal}{\foreign{et~al.}}
\newcommand{\opcit}{\foreign{Op.~cit.}}
\newcommand{\documentname}{\textsl{Article}}
\newcommand{\equationname}{equation}
\newcommand{\bitem}{\begin{itemize}}
\newcommand{\eitem}{\end{itemize}}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}

%% collaborating
\definecolor{dred}{rgb}{0.59,0.,0.09}
\newcommand{\ch}[1]{{\color{dred}{\bf CH:} #1}}

\begin{document}\sloppy\sloppypar\frenchspacing 

\title{Constraining $\smnu$ with the Bispectrum I: Breaking Parameter Degeneracies} 
\date{\texttt{DRAFT~---~\githash~---~\gitdate~---~NOT READY FOR DISTRIBUTION}}

\newcounter{affilcounter}
\author{ChangHoon Hahn}
\altaffiliation{hahn.changhoon@gmail.com}
\affil{Lawrence Berkeley National Laboratory, 1 Cyclotron Rd, Berkeley CA 94720, USA}
\affil{Berkeley Center for Cosmological Physics, University of California, Berkeley, CA 94720, USA}

\author{Francisco Villaescusa-Navarro} 
\affil{Center for Computational Astrophysics, Flatiron Institute, 162 5th Avenue, New York, NY 10010, USA} 

\author{Emanuele Castorina} 
\affil{Berkeley Center for Cosmological Physics, University of California, Berkeley, CA 94720, USA}
\affil{Lawrence Berkeley National Laboratory, 1 Cyclotron Rd, Berkeley CA 94720, USA}

\author{Roman Scoccimarro} 
\affil{Center for Cosmology and Particle Physics, Department of Physics, New York University, NY 10003, New York, USA}

\begin{abstract}
    Massive neutrinos suppress the growth of structure below their free-streaming scale and leave an 
    imprint on large-scale structure. Measuring this imprint allows us to constrain the sum of neutrino 
    masses, $\smnu$, a key parameter in particle physics beyond the Standard Model. However, degeneracies 
    among cosmological parameters, especially between $\smnu$ and $\sig$, limit the constraining power 
    of standard two-point clustering statistics. In this work, we investigate whether we can break these 
    degerancies and constrain $\smnu$ with the next higher-order correlation function --- the bispectrum. 
    We first examine the redshift-space halo bispectrum of $800$ $N$-body simulations from the HADES suite 
    and demonstrate that the bispectrum helps break the $\smnu$--$\sig$ degeneracy. Then using over 42,000
    $N$-body simulations of the Quijote suite, we quantify for the first time the full information content 
    of the redshift-space halo bispectrum down to nonlinear scales using a Fisher matrix forecast of 
    $\{\Om$, $\Ob$, $h$, $n_s$, $\sig$, $\smnu\}$. For $k_{\rm max}{=}0.5~\mpc$, the bispectrum constrains 
    $\Om$, $\Ob$, $h$, $n_s$, and $\sig$ constraints \ch{1.9, 2.7, 3.1, 3.6, and 2.3} times tighter than the 
    power spectrum. For $\smnu$, the bispectrum improves the 1$\sigma$ constraint from 
    \ch{0.1653 to 0.0342 eV --- 5 times tigher than the power spectrum}. Even with priors from {\em Planck}, 
    the bispectrum improves $\smnu$ constraints by a factor of 2.7. Although we reserve marginalizing 
    over \ch{a more complete set of} bias parameters to the next paper of the series, these constraints 
    are derived for a $(1~h^{-1}{\rm Gpc})^3$ box, a substantially smaller volume than upcoming surveys. 
    Thus, our results demonstrate that the bispectrum offers significant improvements over the power 
    spectrum, especially for constraining $\smnu$.  
\end{abstract}

\keywords{
cosmology: cosmological parameters 
--- 
cosmology: large-scale structure of Universe.
---
cosmology: theory
}

% --- intro ---
\input{intro.tex}

% --- hades+quijote ---
\input{sims.tex}

% --- bispectrum ---
\input{bk.tex} 

% --- results ---
\section{Results} \label{sec:results} 
\input{hades.tex} 
\input{quijote.tex} 

% --- summary ---
\input{summary.tex} 

\section*{Acknowledgements}
It's a pleasure to thank 
    Enea Di Dio, 
    Daniel Eisenstein, 
    Simone Ferraro, 
    Shirley Ho, 
    Emmanuel Schaan, 
    Zachary Slepian, 
    David N.~Spergel, 
    and Benjamin D.~Wandelt
    for valuable discussions and comments. 
This material is based upon work supported by the U.S. Department 
of Energy, Office of Science, Office of High Energy Physics, under 
contract No. DE-AC02-05CH11231.
This project used resources of the National Energy Research 
Scientific Computing Center, a DOE Office of Science User 
Facility supported by the Office of Science of the U.S. 
Department of Energy under Contract No. DE-AC02-05CH11231.

\appendix
\input{rsd.tex} 
\input{converge.tex}

\bibliographystyle{yahapj}
\bibliography{emanu} 
\end{document}
