\documentclass[12pt, letterpaper, preprint]{aastex62}
\input{vc}
%\usepackage[breaklinks,colorlinks, urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{color}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{ctable}
\usepackage{bm}
\usepackage[normalem]{ulem} % Added by MS for \sout -> not required for final version
\usepackage{xspace}
\usepackage{csvsimple} 

% typesetting shih
\linespread{1.08} % close to 10/13 spacing
\setlength{\parindent}{1.08\baselineskip} % Bringhurst
\setlength{\parskip}{0ex}
\let\oldbibliography\thebibliography % killin' me.
\renewcommand{\thebibliography}[1]{%
  \oldbibliography{#1}%
  \setlength{\itemsep}{0pt}%
  \setlength{\parsep}{0pt}%
  \setlength{\parskip}{0pt}%
  \setlength{\bibsep}{0ex}
  \raggedright
}
\setlength{\footnotesep}{0ex} % seriously?

% math shih
\newcommand{\setof}[1]{\left\{{#1}\right\}}
\newcommand{\given}{\,|\,}
\newcommand{\lss}{{\small{LSS}}\xspace}

\newcommand{\lcdm}{$\Lambda$CDM} 
\newcommand{\Om}{\Omega_{\rm m}} 
\newcommand{\Ob}{\Omega_{\rm b}} 
\newcommand{\OL}{\Omega_\Lambda}
\newcommand{\smnu}{M_\nu}
\newcommand{\sig}{\sigma_8} 
\newcommand{\mmin}{M_{\rm min}}
\newcommand{\BOk}{\widehat{B}_0} 
\newcommand{\hmpc}{\,h/\mathrm{Mpc}}
\newcommand{\bfi}[1]{\textbf{\textit{#1}}}
\newcommand{\parti}[1]{\frac{\partial #1}{\partial \theta_i}}
\newcommand{\partj}[1]{\frac{\partial #1}{\partial \theta_j}}
\newcommand{\mpc}{h/{\rm Mpc}}

% specific to this project
\newcommand{\quij}{{\sc Quijote}~}
\newcommand{\planck}{{\em Planck}~}
\newcommand{\kmax}{k_{\rm max}}
\newcommand{\Pg}{P^g} 
\newcommand{\Pgl}{P^g_{\ell}} 
\newcommand{\Bg}{B^g_0} 
\newcommand{\Phl}{P^h_{\ell}} 
\newcommand{\Bh}{B^h_0} 

\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
% text shih
\newcommand{\foreign}[1]{\textsl{#1}}
\newcommand{\etal}{\foreign{et~al.}}
\newcommand{\opcit}{\foreign{Op.~cit.}}
\newcommand{\documentname}{\textsl{Article}}
\newcommand{\equationname}{equation}
\newcommand{\bitem}{\begin{itemize}}
\newcommand{\eitem}{\end{itemize}}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\eg}{\emph{e.g.}~}
\newcommand{\ie}{\emph{i.e.}~}

%% collaborating
\newcommand{\todo}[1]{\marginpar{\color{red}TODO}{\color{red}#1}}
\definecolor{orange}{rgb}{1,0.5,0}
\newcommand{\ch}[1]{{\color{orange}{\bf CH:} #1}}

\begin{document}\sloppy\sloppypar\frenchspacing 

\title{Constraining $\smnu$ with the Bispectrum II: the Information Content of the Galaxy Bispectrum} 
\date{\texttt{DRAFT~---~\githash~---~\gitdate~---~NOT READY FOR DISTRIBUTION}}

\newcounter{affilcounter}
\author{ChangHoon Hahn}
\altaffiliation{hahn.changhoon@gmail.com}
\affil{Lawrence Berkeley National Laboratory, 1 Cyclotron Rd, Berkeley CA 94720, USA}
\affil{Berkeley Center for Cosmological Physics, University of California, Berkeley, CA 94720, USA}

\author{Francisco Villaescusa-Navarro} 
\affil{Center for Computational Astrophysics, Flatiron Institute, 162 5th Avenue, New York, NY 10010, USA} 
\affil{Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton NJ 08544, USA} 

\author{...}

\begin{abstract}
    Massive neutrinos suppress the growth of structure below their
    free-streaming scale and leave an imprint on large-scale structure, which
    can be measured to constrain their total mass, $\smnu$. While $\smnu$
    measurements from standard two-point clustering statistics are limited by
    degeneracies with other cosmological parameters, \cite{hahn2020}
    demonstrated that the halo bispectrum, the next higher-order statistic,
    can break these degeneracies and dramatically improve constraints on
    $\smnu$ and other cosmological parameters. 
    % Their forecast, however, did not include a complete galaxy bias model
    % which must be included to infer cosmological parameters from galaxy
    % surveys in pracitce.  
    In practice, however, galaxy bias must be included to infer cosmological 
    parameters from galaxy surveys. The halo occupation distribution (HOD)
    framework, provides an effective galaxy bias framework particularly well 
    suited for a simulation-based approach. Using $195,000$ mock galaxy catalogs 
    constructed from the \quij suite of $N$-body simulations, we incorporate 
    an HOD model and measure Fisher matrix forecast of 
    $\{\Om$, $\Ob$, $h$, $n_s$, $\sig$, $\smnu\}$. % to determine the potential of the {\em galaxy} bispectrum for constraining $\smnu$ and other cosmological parameters, 
    With our forecasts, we quantify for the first time, the total information 
    content of the redshift-space {\em galaxy} bispectrum down to nonlinear 
    scales. For $\kmax=0.5\hmpc$, with the galaxy bispectrum, even after 
    marginalizing HOD parameters, constraints on $\Om$, $\Ob$, $h$, $n_s$, $\sig$ improve by 
    \ch{3.3, 3.6, 4.5, 4.9, and 4.7} from power spectrum constraints. For
    $\smnu$, we derive $5.6\times$ tighter constraints with the bispectrum.
    Including priors from \planck, the bispectrum improves cosmological 
    constraints by \ch{$\gtrsim 2\times$}. While effects such as survey geometry 
    will likely impact the results in reality, these constraints are derived for 
    a substantially smaller volume than upcoming surveys ($(1~h^{-1}{\rm Gpc})^3$ box). 
    Therefore, we safely conclude that including the galaxy bispectrum will 
    significantly improve cosmological constraints, especially $\smnu$, for 
    upcoming galaxy surveys.
\end{abstract}

\keywords{
cosmology: cosmological parameters 
--- 
cosmology: large-scale structure of Universe.
---
cosmology: theory
}

% --- intro ---
\input{intro.tex}

% --- quijote ---
\input{sims.tex}

% --- hod ---
\input{hod.tex} 

% --- methods ---
\input{methods.tex}

% --- results ---
\input{results.tex}

% --- summary ---
\input{summary.tex} 

\section*{Acknowledgements}
It's a pleasure to thank 
    Mehmet Alpaslan, 
    Arka Banerjee, 
    Joseph DeRose, 
    Mikhail Ivanov, 
    Elena Massara,
    Jeremy L. Tinker,
    Roman Scoccimarro, 
    Uro{\u s}~Seljak,
    Zachary Slepian, 
    Digvijay Wadekar,
    Risa Wechsler
    ...
for valuable discussions and comments. 

\appendix

\bibliographystyle{yahapj}
\bibliography{emanu_hod} 
\end{document}
